Hypertension and microbiome

### 2019-01-23 articletwo.Rmd
Minor

@@

```{r Importing functions}
source("aaro/edgeR_plot_functions.R", echo = TRUE)
source("rrbiomefunctions.R", echo = TRUE)

writetable <- function(doc, tbl,  head, foot) {
    doc <- doc %>% 
        body_add_fpar(fpar(ftext("Table . ", prop = text.bold), ftext(head, prop = text.normal)), style = "Table Caption") %>%
        body_add_flextable(tbl, align = "left") %>%
        body_add_par(foot, style = "footnote text") %>%
        body_add_break(pos = "after")
}

>>>>

### RR biome functions

```{r RR biome functions, code=readLines("articletwo-rrbiome.R")}
source("articletwo-rrbiome.R")
```

### EdgeR plot functions

```{r EdgeR functions, code=readLines("aaro/edgeR_plot_functions.R")}
source("aaro/edgeR_plot_functions.R")
```

@@

```{r Importing functions}
writetable <- function(doc, tbl,  head, foot) {
    doc <- doc %>% 
        body_add_fpar(fpar(ftext("Table . ", prop = text.bold), ftext(head, prop = text.normal)), style = "Table Caption") %>%
        body_add_flextable(tbl, align = "left") %>%
        body_add_par(foot, style = "footnote text") %>%
        body_add_break(pos = "after")
}
